### 2022-04-25 LaTeX_Plos/ResponseToReviewers.tex

\begin{document}

\begin{letter}{}

\opening{Dear Dr.~Editor:}

We thank the five reviewers for their evaluation of our manuscript and generally favorable reviews.  
%which has helped us revise the manuscript.  %Both reviewers mention previous research that has been performed on  silver nanoparticles in textiles.  It should be emphasized that our research focuses on reactive silver inks for textiles and their improved antiviral performance and wash durability compared to silver nanoparticles.
%Our work focuses on antiviral activity after washing, which has not been previously reported for silver nanoparticles and ink.  
%Additionally, in our submitted paper, we test the fabric treatments after extended bleach washing with a harsh ultrasonication washing procedure under high concentration bleach (10\%) which has not been previously reported. 
%to allow our work to be of interest 
%to the readership of ACS Applied Nano Materials.
% We thank the three reviewers for their evaluation of our manuscript and comments.  
%We thank the reviewers' statements that ``this review article is comprehensive to introduce the various sources of bio-inspiration, the critical performance requirements and the strategies that have been carried out to tackle the challenges" and we have provided ``an elaborate and comprehensive arrangement of various transparent substrates and barrier layers for optoelectronics." 
We have made improvements to our paper based on the reviewers' comments and suggestions.
Below, we summarize the changes that have been made and respond to the reviewers' comments.
Considering the importance of the topic of this
article on 
%for application of 
bleach washable, anti-viral fabric coatings,
we resubmit this manuscript for your consideration of publication in PLOS One.
Thank you for your consideration.

@@

\blue{The submission portal will not allow us to  add Melbs as an author because his affiliation is not recognized. Can his affiliation be added to the system or added manually?}

\textbf{Additional Editor Comments:}

This manuscript reports the use of reactive inks containing silver nanoparticles for improving antiviral, hydrophobic properties and durability (against harsh washing) of medical textiles. It is an interesting study for wider readership of scientific community working in medical textiles, nanotechnology and polymers. However, it requires revision before it can be considered further.

\blue{We thank the editor for recognizing the importance of our work in the fields of medical textiles, nanotechnology, and polymers.  We have revised the manuscript based on the editor and reviewers' suggestions.}

@@

\blue{We do not see issue here. }

101 The x-axis of the XRD pattern should change to (2$\theta$ (°)). Please at Y-axis please remove numbers if it is going to be reported by Arbitrary unit or remove (a.u.).

\blue{The axes have been changed. }

104 Author mentioned that the untreated PET is fully wetted by water and Fig 2 (a) shows that the water static, contact angle, for PET is zero. Although other studies such as the Indian Journal of Fibre \& Textile Research Vol. 37, September 2012, pp. 287-291 showed the water contact angle of untreated PET fabric is 124.24$\degree$.

### 2022-04-25 LaTeX_Plos/PlosOne.tex
Updates from Overleaf

\section*{Abstract}
%During the most recent virus pandemic, the shortage of personal protective equipment (PPE) became a global health crisis. 
% There is a major need to improve reusable personal protective equipment (PPE) with %virus inhibiting 
% anti-viral
% and liquid repelling functionality. %reusability  and durability for economical and environmental concerns. 
% Silver is a popular coating material to incorporate virus inactivation functionality to PPE. 
Medical textiles are subject to particularly harsh disinfection procedures 
%due to the 
%need to create sterile surfaces 
in healthcare settings where exposure risks are high.  
%high risks of exposure to microbes in healthcare settings.  
This work demonstrates a fabric treatment consisting of 
a reactive silver ink and low surface energy polymer that 
provides for 
superhydrophobicity and antiviral properties against enveloped virus stocks 
even after extended ultrasonic bleach washing. The antiviral properties of reactive silver ink has not been previously reported or compared with silver nanoparticles.
%as well as 
%bleach and ultrasonic cleaning.
%wash 
%durability.  
%a bleach wash durable fabric treatment with . 
The fabric treatment 
exhibits high static contact angles and low contact angle hysteresis with water, even after 300 minutes of ultrasonic bleach washing. Similarly, after this bleach washing treatment, the fabric treatment shows reductions of infectious virus quantities by about 2 logs compared to controls for enveloped viruses. The use of silver ink provides for 
better antiviral efficacy and durability compared to silver nanoparticles due to the use of reactive ionic silver, which demonstrates more conformal coverage of fabric microfibers and better %microfiber 
adhesion.  This study provides insights for improving the wash durability of antiviral silver fabric treatments and demonstrates a bleach wash durable, repellent antiviral treatment for reusable, functional personal protective equipment applications.

@@

%Silver ink is a promising alternative for fabric treatments; however, the functionality durability of silver treated fabrics after bleach washing has not been investigated. 
% The use of silver for functional PPE applications must be durable so that 
% functionality is retained after repeated bleach washing.  
This work studies the virucidal activity of single knit
polyethylene terephthalate (PET) fabrics coated with a silver amine complex ink \cite{Walker:12}
against herpes simplex viruses (HSV-1). This is the first report in literature where reactive silver inks have been considered in developing antiviral medical fabrics. We investigate and discuss the advantages of silver inks compared to silver nanoparticles for reusable antiviral medical fabrics. 
%Once the silver ink is cured on the fabric, the additional ingredients \commentPaul{Be more specific} \commentsAnthony{These ingredients are proprietary. We could take this sentence out.} of the ink evaporate to leave a pure silver film.   
%The ink is cured thermally
PET fabric material is commonly used for medical and healthcare applications such as gowns, scrubs and caps due to its low cost, elasticity and durability  \cite{Rigby:97}. 
HSV-1 is an enveloped virus about 160 nm in diameter that can cause cold sores and blinding herpetic eye infections \cite{wald:07}. 
The attachment and entry of HSV-1 into cells require the interaction between the viral envelope glycoproteins and cell surface heparan sulfate (HS) \cite{baram-pinto_2009,akbarzadeh:2018}. Silver mimics HS and competes for binding sites of the virus to the cell, inhibiting the virus from cell attachment and entry \cite{baram-pinto_2009,Galdiero:11}.

We show that the reactive silver ink provides better antiviral and bleach wash durability compared to 20 nm diameter silver nanoparticles. The size of the silver nanoparticles is considered as it is the maximum size to offer virus inhibition with HSV-1 and HIV-1  \cite{akbarzadeh:2018,elechiguerra_interaction_2005}. Also, silver nanoparticles of similar size are shown to inhibit human coronavirus on mask fabric \cite{abulikemu:2022}.

@@

However, we observe the performance of both silver fabric treatments can be significantly hindered after extended periods of ultrasonic bleach washing. 
%\commentPaul{Any ideas on the mechanism why reactive silver ink would be able to inactivate but silver nanoparticles not.}
%\commentPaul{Give percentage.}
%\commentPaul{Give $p$ number from t-test?}
%$2.3 \pm 0.8$ log, $2.7 \pm 0.8$ log, $2.7 \pm 0.8$ log and $2.8 \pm 0.7$ log PFU per mL, respectively.
%for enhanced stability. 
% In this work, we compare the anti-viral properties of a reactive silver ink in phosphate buffered saline (PBS) and on polyester (PET) fabric with silver nanoparticles. 
An additional polydimethylsiloxane (PDMS) thin film is used protect the silver layer and increase the liquid repellent properties of the fabric to further improve %decontamination
the bleach wash durability of the antiviral functionality. 
%The antiviral property of silver-PDMS fabric treatments after washing with bleach has not been tested previously.
When the silver layer is protected by the polymer, the silver ink treated fabric retains 42\% more silver than silver nanoparticle treated fabrics after bleach washing.
PET fabric samples coated with reactive silver ink and PDMS reduce virus quantities by $1.7 \pm 0.2$ log$_{10}$ ($98.2 %\pm 0.8 
\%$, $p < 0.01$) after 300 minutes of ultrasonic bleach washing. 
We demonstrate the combination of reactive silver ink with PDMS as a PET fabric treatment that adds durable, superhydrophobic and antiviral properties for reusable PPE applications.

@@

\begin{figure}[!h]
\caption{{\bf Sample characterization of silver coated fabric.}
a) Schematic of silver treatment on PET fabric (b-d) SEM images of b) untreated PET c) PET-NP and d) PET-Ink. e-f) XRD spectra of e) PET-NP and f) PET-Ink samples.}
\label{fig1}
\end{figure}

@@

Ultrasonic bleach washing experiments are performed to assess the durability of silver.  
The cumulative percentage of silver that comes off coated samples during bleach washing is shown in 
Fig~\ref{fig2}b. The silver concentration from the affluent of each 30 minute washing cycle is measured using inductively coupled plasma mass spectrometry (ICP-MS). 
PET-NP samples lose $62 \pm 9$\% of the coated silver after the first 30 minutes of washing. 
PET-Ink samples lose silver at a slower rate due to the more uniform coating and stronger attachment to the PET from the silver ink diamine complex. 
Both treatments lose at least 99\% of the silver by 120 minutes of ultrasonic bleach washing. 
Fig~\ref{fig2}c shows representative images of the (i) PET-NP and (ii) PET-Ink samples as a function of bleach washing cycles.  
%Bleach oxidizes silver, which degrades the intrinsic properties. 
The combination of ultrasonic agitation and bleach not only mechanically removes silver from the textile but chemically oxidizes the silver.  
It is evident that silver treated fabrics need additional surface treatment for reuse in bleach washing procedures.

Additonally, we investigate the anti-viral activity of the silver coatings in solution (Fig~\ref{fig2}c). 
Virus assays in saline are conducted by mixing silver ink or silver nanoparticles (0.1\%) in phosphate buffered saline (PBS) with HSV-1 in PBS for 1 hour, followed by centrifuging, removing the supernatant, and quantifying the amount of remaining virus using plaque forming units (PFU). 
Fig~\ref{fig2}d shows the virus inactivation results of silver nanoparticles and silver reactive ink
%-coated PET  %-coated PET 
with enveloped HSV-1 in PBS at a concentration of 1 mg per mL (0.1\%). 
%While the 
20 nm silver nanoparticles do not show HSV-1 inactivation with a $0.0 \pm 0.1$ log$_{10}$ difference, while the silver ink shows HSV-1 inactivation in saline by $1.6 \pm 0.9$ log$_{10}$ ($97.3 %\pm 5.5 
\%$) difference. 
%\commentPaul{Give percentage.}
Previous reports have suggested that virus inactivation is stronger with smaller diameter silver nanoparticles ($\leq$ 15 nm) and it is possible the nanoparticles are too large to cover the binding sites of HSV-1 to inhibit cell entry.\cite{jeremiah_potent_2020}
% It is possible the size of the nanoparticles are too large to cover the glycoprotein binding sites on the HSV envelope to inhibit virus activity. 
In contrast, the reactive silver ink %shows more HSV-1 inactivation because it
consists of reactive ionic silver which can form molecular clusters ($<$ 3 nm) that may be able to better coat the binding sites of HSV and thus, provide for more virus inactivation.

@@

A PDMS post treatment is added to the silver coated samples to improve the ultrasonic bleach wash durability. PDMS is a low surface energy polymer that offers liquid repellent properties to fabrics.\cite{ye_2018} 
%\commentPaul{reference?}
%Also, PDMS does not react heavily with bleach to provide chemical resistance. 
PDMS enhances the adhesion of the silver to the underlying microfibers by increasing the area of contact between the silver and textile as well as providing some chemical resistance.  
Both PET-NP and PET-Ink samples are dipped in PDMS (1:10 curing agent:PDMS ratio, Sylgard 184) dissolved in hexane and cured in an oven at 150 \degree C for two hours to make PET-NP/P and PET-I/P samples, respectively. 
%The PDMS coating improves the liquid repellency and silver retention of fabric samples.

Fig~\ref{fig3} shows the characterization of PET-NP/P and PET-I/P samples. A schematic of the  PDMS treatment process is depicted in Fig~\ref{fig3}a.
%\commentPaul{Short description of process.  Follow template for Figure 1.  Use parentheses for all subfigures.}
%lists the water static contact angle, hysteresis and breakthrough pressure for respective samples. 
%\figref[b-c]{fig:wet} shows 
SEM imaging shows the physical morphology of microfibers for PET-NP/P (Fig~\ref{fig3}b) and PET-I/P (Fig~\ref{fig3}c) samples. The PDMS layer can be observed on the microfibers for both treatments. The PDMS coating appears roughened due to the underlying morphology of the silver nanoparticles or silver ink coated fabrics.
XRD spectroscopy identifies the crystalline phases present on PET-NP/P (Fig~\ref{fig3}d) and PET-I/P (Fig~\ref{fig3}e) microfibers before and after PDMS coating. The distinct silver peaks of (111) and (200) are still present for both samples after the PDMS coating, confirming the presence of silver on the samples. The PDMS coating adds broader peaks at $2\theta = 22-27\degree$~due to the amorphous polymer structure. 
%\commentPaul{More discussion of difference without PDMS.}

\begin{figure}[!h]
\caption{{\bf Characterization of samples with PDMS}{
a) Schematic of PDMS treatment for silver coated PET samples (b-c) SEM images of treated fiber of b) PET-NP/P and c) PET-I/P samples. d-e) XRD spectra of fabric samples before and after PDMS coating for d) PET-NP/P with PET-NP and e) PET-I/P with PET-Ink samples.}}
\label{fig3}
\end{figure}

@@

The PDMS layer is structurally damaged during bleach washing, which regulates the controlled release of silver after washing. The PDMS layer for both samples appear rougher after 300 minutes of bleach washing from SEM images (Fig~\ref{fig4}e). Loss of PDMS as well as cracking can be seen.  
XRD spectra of samples after bleach washing shows new distinct peaks observed at 2$\theta =$ 27.8\degree, 32.3\degree and 46.3\degree corresponding to the (111), (200) and (220) crystal planes, respectively, of silver chloride (\nameref{S2_Fig}). 
Some of the silver is exposed to the bleach solution due to damage to the PDMS layer and reacts into silver chloride. %and the PDMS layer appears rougher after washing from SEM images (\figref[e]{fig:durable2}) . 
PET is coated with PDMS only and washed to further investigate the structural integrity of the PDMS layer after bleach washing (\nameref{S3_Fig}). The static contact angle increases after bleach washing, confirming the roughening of the PDMS layer. No oxidation of the PDMS layer from bleach washing is observed using FTIR analysis, so the damage to the PDMS is believed to be primarily caused by cavitation during ultrasonic agitation. These findings suggest that some damage to the PDMS layer and the silver layer occurs from ultrasonic washing with bleach.   
%\commentPaul{Discuss new XRD peaks.  Possible Ag chloride?}

@@

\section*{Materials and Methods}
%\subsection{Sample Preparation}
Materials: PET single knit cleanroom wipes (Anticon Gold), acetone (99.5\%), methanol (99.9\%) and isopropyl alcohol (99.5\%) were bought from VWR.  PBS, FBS, PDMS (Sylgard 184) and hexane were bought from Sigma-Aldrich. Reactive silver inks (720 series, approx. 20\% silver) was provided by Electroninks. Silver nanoparticles (20 nm, 1mg/mL in sodium citrate) were purchased from NanoComposix. Household bleach (Giant Eagle brand) was purchased from Giant Eagle. Deionized water was used from a Millipore Academic A10 system with total organic carbon below 40 ppb. Herpes simplex virus were obtained from a clinical isolate of HSV-1 Mckrae and frozen at -70 \degree C. Virus stocks in PBS were prepared with A549 human lung carcinoma cells. The virus stocks were diluted in sterile PBS to the experimental titers used.

Sample Fabrication: 0.5 in.~by 0.5 in.~square samples were cut from PET fabric. All samples were rinsed with acetone, methanol and isopropyl alcohol and dried with nitrogen to eliminate possible contaminants. An equal amount of 0.2mg of silver was added to fabric samples, confirmed by microscale after curing. Silver ink was added by drop casting onto untreated PET fabrics followed by oven curing for 1 hour at 120 \degree C to make PET-Ink samples. Silver nanoparticles was added by drop casting onto untreated PET fabrics followed by oven curing for 1 hour at 120 \degree C to make PET-NP samples. Additional PET-Ink and PET-NP samples were treated with a PDMS layer by soaking samples in PDMS (Sylgard 184) at 1:10 curing agent:PDMS ratio dissolved in hexane and curing for two hours at 150 \degree C to make PET-I/P and PET-NP/P samples, respectively.

Sample Characterization: The physical morphologies of samples were characterized by scanning electron microscopy (SEM, Zeiss Sigma 500 VP) at 5kV. For SEM imaging, all samples were sputter coated with 10 nm gold/palladium (80:20) using a sputter coater (Denton). The presence of silver was confirmed using X-ray diffraction (XRD) locked coupled continuous scan at voltage 40kV, current 40mA and step size 0.04 degrees. The chemical compositions of samples were characterized by Fourier transform infrared spectroscopy (FTIR, Bruker Vertex-70LS) between 600 and 3200 cm$^{-1}$ wavelengths using 16 scans.

Static, advancing and receding contact angle measurements were taken in ambient air at 22–25°C and 20–30\% relative humidity using an optical tensiometer (Attension, 811 Theta). 5 \micro L droplets at 25°C for all test liquids were used for all wetting measurements. The hysteresis was tabulated for each treatment after measuring the advancing and receding contact angles during syringe-controlled water dispersion and withdrawal, respectively.

@@

Durability Testing: Washing cycles were performed using a Powersonic P230 Ultrasonic Cleaner (Crest) under ASTM G131-96 standards for washing materials by ultrasonic techniques. 10\% bleach washing solution was prepared in a 10 mL test tube to create a highly efficient washing solution. Samples were submerged in bleach solution in Eppendorf tubes and ultrasonicated for 30 minutes at 80 W and 54°C to complete one wash cycle. Afterwards, samples were dried in ambient temperature before testing.

@@

Virus Assays: Virus inactivation assays were performed by mixing silver nanoparticles or silver ink with  herpes virus in PBS at final silver concentration of 1 mg per mL (0.1\% v/v). Solutions were vortexed and incubated for 1 hour %while shaking for 60 minutes (Stoval Belly Dancer, level 7) 
at room temperature. After 1 hour of incubation, 500 \micro l of ice-cold tissue culture media containing 20\% FBS was added, then vortexed and centrifuged for 1 minute in the Eppendorf centrifuge to pellet any silver. The supernatants were removed and plated with 0.1 ml of serial 10-fold dilutions in duplicate onto A549 monolayers in 24 well multiplates. The virus was absorbed for 1-3 hours after which the wells were filled with 1 ml of tissue culture media containing 0.5\% methyl cellulose.  Plates were incubated for 5-6 days in 5\% CO2 and then fixed and stained with 0.5\% gentian violet solution containing formalin and the plaques were quantified.

Assays on Fabrics: Fabric samples were completely submerged in 0.4 mL of virus/PBS in Eppendorf tubes with moderate shaking for 60 minutes (Stoval Belly Dancer, level 5) at room temperature. %Adenovirus/PBS inoculum titers were averaged as 1.6x105 and 1.4x104 PFU mL−1 for types 4 and 7a viruses, respec-tively. 
After shaking, samples were gingerly rinsed once in sterile PBS and submerged in Eppendorf tubes with 0.4 mL of PBS. Then, virions attached on the surface were removed from the samples into PBS by sonication at power 3 for 10 seconds (Qsonica, Model Q55) within the tubes. The remaining PBS was used to quantify plaques.

>>>>

\section*{Abstract}
%During the most recent virus pandemic, the shortage of personal protective equipment (PPE) became a global health crisis. 
% There is a major need to improve reusable personal protective equipment (PPE) with %virus inhibiting 
% anti-viral
% and liquid repelling functionality. %reusability  and durability for economical and environmental concerns. 
% Silver is a popular coating material to incorporate virus inactivation functionality to PPE. 
Medical textiles are subject to particularly harsh disinfection procedures 
%due to the 
%need to create sterile surfaces 
in healthcare settings where exposure risks are high.  
%high risks of exposure to microbes in healthcare settings.  
This work demonstrates a fabric treatment consisting of 
a reactive silver ink and low surface energy PDMS polymer that 
provides for 
superhydrophobicity and antiviral properties against enveloped herpes simplex virus stocks 
even after extended ultrasonic bleach washing. The antiviral properties of reactive silver ink has not been previously reported or compared with silver nanoparticles.
%as well as 
%bleach and ultrasonic cleaning.
%wash 
%durability.  
%a bleach wash durable fabric treatment with . 
The fabric treatment 
exhibits high static contact angles and low contact angle hysteresis with water, even after 300 minutes of ultrasonic bleach washing. Similarly, after this bleach washing treatment, the fabric treatment shows reductions of infectious virus quantities by about 2 logs compared to controls for enveloped viruses. The use of silver ink provides for 
better antiviral efficacy and durability compared to silver nanoparticles due to the use of reactive ionic silver, which demonstrates more conformal coverage of fabric microfibers and better %microfiber 
adhesion.  This study provides insights for improving the wash durability of antiviral silver fabric treatments and demonstrates a bleach wash durable, repellent antiviral treatment for reusable, functional personal protective equipment applications.

@@

%Silver ink is a promising alternative for fabric treatments; however, the functionality durability of silver treated fabrics after bleach washing has not been investigated. 
% The use of silver for functional PPE applications must be durable so that 
% functionality is retained after repeated bleach washing.  
This work studies the virucidal activity of single knit
polyethylene terephthalate (PET) fabrics coated with a silver amine complex ink \cite{Walker:12}
against herpes simplex viruses (HSV-1). This is the first report in literature where reactive silver inks have been considered in developing antiviral medical fabrics. This work investigates and discusses the advantages of silver inks compared to silver nanoparticles for reusable antiviral medical fabrics. 
%Once the silver ink is cured on the fabric, the additional ingredients \commentPaul{Be more specific} \commentsAnthony{These ingredients are proprietary. We could take this sentence out.} of the ink evaporate to leave a pure silver film.   
%The ink is cured thermally
PET fabric material is commonly used for medical and healthcare applications such as gowns, scrubs and caps due to its low cost, elasticity and durability  \cite{Rigby:97}. 
HSV-1 is an enveloped virus about 160 nm in diameter that can cause cold sores and blinding herpetic eye infections \cite{wald:07}. 
The attachment and entry of HSV-1 into cells require the interaction between the viral envelope glycoproteins and cell surface heparan sulfate (HS) \cite{baram-pinto_2009,akbarzadeh:2018}. Silver mimics HS and competes for binding sites of the virus to the cell, inhibiting the virus from cell attachment and entry \cite{baram-pinto_2009,Galdiero:11}.

The reactive silver ink demonstrates better antiviral and bleach wash durability compared to 20 nm diameter silver nanoparticles. The size of the silver nanoparticles is considered as it is the maximum size to offer virus inhibition with HSV-1 and HIV-1  \cite{akbarzadeh:2018,elechiguerra_interaction_2005}. Also, silver nanoparticles of similar size are shown to inhibit human coronavirus on mask fabric \cite{abulikemu:2022}.

@@

However, the results suggest the performance of both silver fabric treatments can be significantly hindered after extended periods of ultrasonic bleach washing. 
%\commentPaul{Any ideas on the mechanism why reactive silver ink would be able to inactivate but silver nanoparticles not.}
%\commentPaul{Give percentage.}
%\commentPaul{Give $p$ number from t-test?}
%$2.3 \pm 0.8$ log, $2.7 \pm 0.8$ log, $2.7 \pm 0.8$ log and $2.8 \pm 0.7$ log PFU per mL, respectively.
%for enhanced stability. 
% In this work, we compare the anti-viral properties of a reactive silver ink in phosphate buffered saline (PBS) and on polyester (PET) fabric with silver nanoparticles. 
An additional polydimethylsiloxane (PDMS) thin film is used protect the silver layer and increase the liquid repellent properties of the fabric to further improve %decontamination
the bleach wash durability of the antiviral functionality. 
%The antiviral property of silver-PDMS fabric treatments after washing with bleach has not been tested previously.
When the silver layer is protected by the polymer, the silver ink treated fabric retains 42\% more silver than silver nanoparticle treated fabrics after bleach washing.
PET fabric samples coated with reactive silver ink and PDMS reduce virus quantities by $1.7 \pm 0.2$ log$_{10}$ ($98.2 %\pm 0.8 
\%$, $p < 0.01$) after 300 minutes of ultrasonic bleach washing. 
We demonstrate the combination of reactive silver ink with PDMS as a PET fabric treatment that adds durable, superhydrophobic and antiviral properties for reusable PPE applications.

@@

\begin{figure}[!h]
\caption{{\bf Sample characterization of silver coated fabric.}
a) Schematic of silver treatment on PET fabric (b-d) SEM images of b) untreated PET c) PET-NP and d) PET-Ink. e-f) XRD pattern of e) PET-NP and f) PET-Ink samples.}
\label{fig1}
\end{figure}

@@

Ultrasonic bleach washing experiments are performed to assess the durability of silver.  
The cumulative percentage of silver that comes off coated samples during bleach washing is shown in 
Fig~\ref{fig2}b. The silver concentration from the affluent of each 30 minute washing cycle is measured using inductively coupled plasma mass spectrometry (ICP-MS). 
PET-NP samples lose $62 \pm 9$\% of the coated silver after the first 30 minutes of washing. 
PET-Ink samples lose silver at a slower rate due to the more uniform coating and stronger attachment to the PET from the silver ink diamine complex. 
Both treatments lose at least 99\% of the silver by 120 minutes of ultrasonic bleach washing. 
Fig~\ref{fig2}c shows representative images of the (i) PET-NP and (ii) PET-Ink samples as a function of bleach washing cycles.  
%Bleach oxidizes silver, which degrades the intrinsic properties. 
The combination of ultrasonic agitation and bleach not only mechanically removes silver from the textile, but also chemically reacts with silver. % to form silver chloride.  
It is evident that silver treated fabrics need additional surface treatment for reuse in bleach washing procedures.

Additonally, we investigate the anti-viral activity of the silver coatings in solution (Fig~\ref{fig2}c). 
Virus assays in saline are conducted by mixing silver ink or silver nanoparticles (0.1\%) in phosphate buffered saline (PBS) with HSV-1 in PBS for 1 hour, followed by centrifuging, removing the supernatant, and quantifying the amount of remaining virus using plaque forming units (PFU). 
Fig~\ref{fig2}d shows the virus inactivation results of silver nanoparticles and silver reactive ink
%-coated PET  %-coated PET 
with enveloped HSV-1 in PBS at a concentration of 1 mg per mL (0.1\%). 
%While the 
20 nm silver nanoparticle coating does not show HSV-1 inactivation with a $0.0 \pm 0.1$ log$_{10}$ difference, while the silver ink shows HSV-1 inactivation in saline by $1.6 \pm 0.9$ log$_{10}$ ($97.3 %\pm 5.5 
\%$) difference. 
%\commentPaul{Give percentage.}
Previous reports have suggested that virus inactivation is stronger with smaller diameter silver nanoparticles ($\leq$ 15 nm) and it is possible the nanoparticles are too large to cover the binding sites of HSV-1 to inhibit cell entry.\cite{jeremiah_potent_2020}
% It is possible the size of the nanoparticles are too large to cover the glycoprotein binding sites on the HSV envelope to inhibit virus activity. 
In contrast, the reactive silver ink %shows more HSV-1 inactivation because it
consists of reactive ionic silver which can form molecular clusters ($<$ 3 nm) that may be able to better coat the binding sites of HSV and thus, provide for more virus inactivation.

@@

A PDMS post treatment is added to the silver coated samples to improve the ultrasonic bleach wash durability. PDMS is a low surface energy polymer that offers liquid repellent and chemical resistance properties to fabrics.\cite{ye_2018} 
%\commentPaul{reference?}
%Also, PDMS does not react heavily with bleach to provide chemical resistance. 
%PDMS improves the liq the adhesion of the silver to the underlying microfibers by increasing the area of contact between the silver and textile as well as providing some chemical resistance.
Both PET-NP and PET-Ink samples are dipped in PDMS (1:10 curing agent:PDMS ratio, Sylgard 184) dissolved in hexane and cured in an oven at 150 \degree C for two hours to make PET-NP/P and PET-I/P samples, respectively. 
%The PDMS coating improves the liquid repellency and silver retention of fabric samples.

Fig~\ref{fig3} shows the characterization of PET-NP/P and PET-I/P samples. A schematic of the  PDMS treatment process is depicted in Fig~\ref{fig3}a.
%\commentPaul{Short description of process.  Follow template for Figure 1.  Use parentheses for all subfigures.}
%lists the water static contact angle, hysteresis and breakthrough pressure for respective samples. 
%\figref[b-c]{fig:wet} shows 
SEM imaging shows the physical morphology of microfibers for PET-NP/P (Fig~\ref{fig3}b) and PET-I/P (Fig~\ref{fig3}c) samples. The PDMS layer can be observed on the microfibers for both treatments. The PDMS coating appears rough due to the underlying morphology of the silver nanoparticles or silver ink coated fabrics.
XRD characerization technique identifies the crystalline phases present on PET-NP/P (Fig~\ref{fig3}d) and PET-I/P (Fig~\ref{fig3}e) microfibers before and after PDMS coating. The distinct silver peaks of (111) and (200) are still present for both samples after the PDMS coating, confirming the presence of silver on the samples. The PDMS coating adds broader peaks at $2\theta = 22-27\degree$~due to the amorphous polymer structure. 
%\commentPaul{More discussion of difference without PDMS.}

\begin{figure}[!h]
\caption{{\bf Characterization of samples with PDMS}{
a) Schematic of PDMS treatment for silver coated PET samples (b-c) SEM images of treated fiber of b) PET-NP/P and c) PET-I/P samples. d-e) XRD patterns of fabric samples before and after PDMS coating for d) PET-NP/P with PET-NP and e) PET-I/P with PET-Ink samples.}}
\label{fig3}
\end{figure}

@@

The PDMS layer is structurally damaged during bleach washing, which regulates the controlled release of silver after washing. The PDMS layer for both samples appear rougher after 300 minutes of bleach washing from SEM images (Fig~\ref{fig4}e). Loss of PDMS as well as cracking can be seen.  
XRD patterns of samples after bleach washing shows new distinct peaks observed at 2$\theta =$ 27.8\degree, 32.3\degree and 46.3\degree corresponding to the (111), (200) and (220) crystal planes, respectively, of silver chloride (\nameref{S2_Fig}). 
Some of the silver is exposed to the bleach solution due to damage to the PDMS layer and reacts into silver chloride. %and the PDMS layer appears rougher after washing from SEM images (\figref[e]{fig:durable2}) . 
PET is coated with PDMS only and washed to further investigate the structural integrity of the PDMS layer after bleach washing (\nameref{S3_Fig}). The static contact angle increases after bleach washing, confirming the roughening of the PDMS layer. No oxidation of the PDMS layer from bleach washing is observed using FTIR analysis, so the damage to the PDMS is believed to be primarily caused by cavitation during ultrasonic agitation. These findings suggest that some damage to the PDMS layer and the silver layer occurs from ultrasonic washing with bleach.   
%\commentPaul{Discuss new XRD peaks.  Possible Ag chloride?}

@@

\section*{Materials and Methods}
%\subsection{Sample Preparation}
Materials: PET single knit cleanroom wipes (Anticon Gold), acetone (99.5\%), methanol (99.9\%) and isopropyl alcohol (99.5\%) were bought from VWR.  PBS, FBS, PDMS (Sylgard 184) and hexane were bought from Sigma-Aldrich. Reactive silver inks (720 series, approx. 20\% silver) was provided by Electroninks. Silver nanoparticles (20 nm, 1 mg/mL in sodium citrate) were purchased from NanoComposix. Household bleach (Giant Eagle brand) was purchased from Giant Eagle. Deionized water was used from a Millipore Academic A10 system with total organic carbon below 40 ppb. Herpes simplex virus were obtained from a clinical isolate of HSV-1 Mckrae and frozen at -70 \degree C. Virus stocks in PBS were prepared with A549 human lung carcinoma cells. The virus stocks were diluted in sterile PBS to the experimental titers used.

Sample Fabrication: 0.5 in.~by 0.5 in.~square samples were cut from PET fabric. All samples were rinsed with acetone, methanol and isopropyl alcohol and dried with nitrogen to eliminate possible contaminants. An equal amount of 0.2 mg of silver was added to fabric samples, confirmed by microscale after curing. Silver ink was added by drop casting onto untreated PET fabrics followed by oven curing for 1 hour at 120 \degree C to make PET-Ink samples. Silver nanoparticles was added by drop casting onto untreated PET fabrics followed by oven curing for 1 hour at 120 \degree C to make PET-NP samples. Additional PET-Ink and PET-NP samples were treated with a PDMS layer by soaking samples in PDMS (Sylgard 184) at 1:10 curing agent:PDMS ratio dissolved in hexane and curing for two hours at 150 \degree C to make PET-I/P and PET-NP/P samples, respectively.

Sample Characterization: The physical morphologies of samples were characterized by scanning electron microscopy (SEM, Zeiss Sigma 500 VP) at 5 kV. For SEM imaging, all samples were sputter coated with 10 nm gold/palladium (80:20) using a sputter coater (Denton). The presence of silver was confirmed using X-ray diffraction (XRD, Bruker D8) locked coupled continuous scan at voltage 40 kV, current 40 mA and step size 0.04 degrees. The chemical compositions of samples were characterized by Fourier transform infrared spectroscopy (FTIR, Bruker Vertex-70LS) between wavenumber 600 and 3200 cm$^{-1}$  using 16 scans.

Static, advancing and receding contact angle measurements were taken in ambient air at 22–25 \degree C and 20–30\% relative humidity using an optical tensiometer (Attension, 811 Theta). 5 \micro L droplets at 25 \degree C for all test liquids were used for all wetting measurements. The hysteresis was tabulated for each treatment after measuring the advancing and receding contact angles during syringe-controlled water dispersion and withdrawal, respectively.

@@

Durability Testing: Washing cycles were performed using a Powersonic P230 Ultrasonic Cleaner (Crest) under ASTM G131-96 standards for washing materials by ultrasonic techniques. 10\% bleach washing solution was prepared in a 10 mL test tube to create a highly efficient washing solution. Samples were submerged in bleach solution in Eppendorf tubes and ultrasonicated for 30 minutes at 80 W and 54 \degree C to complete one wash cycle. Afterwards, samples were dried in ambient temperature before testing.

@@

Virus Assays: Virus inactivation assays were performed by mixing silver nanoparticles or silver ink with  herpes virus in PBS at final silver concentration of 1 mg per mL (0.1\% v/v). Solutions were vortexed and incubated for 1 hour %while shaking for 60 minutes (Stoval Belly Dancer, level 7) 
at room temperature. After 1 hour of incubation, 500 \micro L of ice-cold tissue culture media containing 20\% FBS was added, then vortexed and centrifuged for 1 minute in the Eppendorf centrifuge to pellet any silver. The supernatants were removed and plated with 0.1 mL of serial 10-fold dilutions in duplicate onto A549 monolayers in 24 well multiplates. The virus was absorbed for 1-3 hours after which the wells were filled with 1 mL of tissue culture media containing 0.5\% methyl cellulose.  Plates were incubated for 5-6 days in 5\% CO$_2$ and then fixed and stained with 0.5\% gentian violet solution containing formalin and the plaques were quantified.

Assays on Fabrics: Fabric samples were completely submerged in 0.4 mL of virus/PBS in Eppendorf tubes with moderate shaking for 1 hour (Stoval Belly Dancer, level 5) at room temperature. %Adenovirus/PBS inoculum titers were averaged as 1.6x105 and 1.4x104 PFU mL−1 for types 4 and 7a viruses, respec-tively. 
After shaking, samples were gingerly rinsed once in sterile PBS and submerged in Eppendorf tubes with 0.4 mL of PBS. Then, virions attached on the surface were removed from the samples into PBS by sonication at power 3 for 10 seconds (Qsonica, Model Q55) within the tubes. The remaining PBS was used to quantify plaques.
